--
title: "Spatial Analysis and Visualization of BC Protected and Conserved Areas using R and Shiny"
author: "Ivo Arrey"
date: "21/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Used 

Here is the link to the data used in this analysis:

- [**Canadian Protected and Conserved Areas Database**](https://www.canada.ca/en/environment-climate-change/services/national-wildlife-areas/protected-conserved-areas-database.html): SpatialPolygonsDataFrame
- [**Protected Lands and Waters in B.C.**](http://www.env.gov.bc.ca/soe/indicators/land/protected-lands-and-waters.html): multipolygons

### Rationale for Data
Why I used this data:

1. *Updated*
2. *Relevant and interesting*


# Load packages
```{r, message=FALSE, warning=FALSE}
library(sf)
library(ggplot2)
library(dplyr)
library(bcmaps)
library(rgdal)
library(envreportutils)
```

# Read and project data
```{r results='hide'}
BC_June2019 <- readRDS('CPCAD_BCJune2019')
BC_June <- readRDS('simplefeatureclass_Dec2019')
BC2 <- readRDS('simplefeatureclass_Dec2018')

areas <- st_transform(areas, 32616)
libraries <- st_transform(libraries, 32616)
```

# Make a ggplot!
```{r map, echo=FALSE, fig.height=2, fig.width=2}
ggplot() +
  geom_sf(data = areas) +
  geom_sf(data = libraries)
```

# A useful shortcut
Use `Ctrl-Alt-I` to insert a code chunk. Or click the "Insert" button at the top of a R Markdown document
