--
title: "Spatial Analysis and Visualization of BC Protected and Conserved Areas using R and Shiny"
author: "Ivo Arrey"
date: "21/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Used 

Here is the link to the data used in this analysis:

- [**Canadian Protected and Conserved Areas Database**](https://www.canada.ca/en/environment-climate-change/services/national-wildlife-areas/protected-conserved-areas-database.html): SpatialPolygonsDataFrame
- **Protected Lands and Waters in B.C.**: multipolygons

### Rationale for Data
Why I used this data:

1. *Different geometries*
2. *Relevant and interesting*


# Load packages
```{r, message=FALSE, warning=FALSE}
library(sf)
library(ggplot2)
library(dplyr)
```

# Read and project data
```{r results='hide'}
areas <- st_read("https://data.cityofchicago.org/resource/igwz-8jzy.geojson")
libraries <- st_read("https://data.cityofchicago.org/resource/psqp-6rmg.geojson")
areas <- st_transform(areas, 32616)
libraries <- st_transform(libraries, 32616)
```

# Make a ggplot!
```{r map, echo=FALSE, fig.height=2, fig.width=2}
ggplot() +
  geom_sf(data = areas) +
  geom_sf(data = libraries)
```

# A useful shortcut
Use `Ctrl-Alt-I` to insert a code chunk. Or click the "Insert" button at the top of a R Markdown document
