--
title: "Spatial Analysis and Visualization of BC Protected and Conserved Areas using R and Shiny"
author: "Ivo Arrey"
date: "21/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Used 

Here is the link to the data used in this analysis:

- [**Canadian Protected and Conserved Areas Database**](https://www.canada.ca/en/environment-climate-change/services/national-wildlife-areas/protected-conserved-areas-database.html): SpatialPolygonsDataFrame
- [**Protected Lands and Waters in B.C.**](http://www.env.gov.bc.ca/soe/indicators/land/protected-lands-and-waters.html): multipolygons

### Rationale for Data
Why I used this data:

1. *Updated*
2. *Relevant and interesting*


# Load packages
```{r, message=FALSE, warning=FALSE}
library(sf)
library(ggplot2)
library(dplyr)
library(bcmaps)
library(rgdal)
library(tmap)
library(leaflet)
library(mapview)
```

The Canadian Protected and Conserved Areas Database (CPCAD) contains the most up to date spatial and attribute data on marine and terrestrial protected areas and other effective area-based conservation measures (OECM) in Canada. It is compiled and managed by Environment and Climate Change Canada (ECCC), in collaboration with federal, provincial, and territorial jurisdictions.

# Read in the Canadian Protected and Conserved Areas Database (CPCAD) filtered for the province of B.C.

```{r results='hide'}

BC_June2019 <- readRDS('D:/BC_Spatial/Code/CPCAD_BCJune2019')
BC_Dec2019 <- readRDS('D:/BC_Spatial/Code/CPCAD_BCDec2019')
BC_June2018 <- readRDS('D:/BC_Spatial/Code/CPCAD_BCDec2018')

```

# Thematic view of B.C territorial boundary map 
```{r }
 bc <- bc_bound()
plot(st_geometry(bc))

```

# Faceted map showing spatial and temporal change in terrestrial and marine Biomes  
```{r}
ma0 <- tm_shape(BC_June2019) + tm_borders() + tm_fill(col = 'BIOME', title = expression("B.C. (June 2019)"))+ tm_style('classic')
ma1 <- tm_shape(BC_Dec2019) + tm_borders() + tm_fill(col = 'BIOME', title = expression("B.C (December 2019)"))+ tm_style('classic')
ma2 <- tm_shape(BC_June2018)+ tm_borders() + tm_fill(col = 'BIOME', title = expression("B.C. (June 2018)"))+ tm_style('classic')
tmap_arrange(ma0,ma1,ma2)

```


# Analyse the changes in percentage of terrestrial and marine protected and conserved areas over time

## percentage change of terrestrial protected and conserved areas in B.C from June 2018 to December 2019

```{r}
BiomeT_June2018 <- BC_June2018 %>% filter(BIOME == 'T')%>% group_by(TYPE_E)%>% summarise(area_des_ha = as.numeric(sum(O_AREA)) * 1e-4) %>%
    mutate(percent_des = (area_des_ha * 1e4) / as.numeric(sum(BC_Dec2019$O_AREA)) * 100) %>%
    mutate_if(is.numeric, round, digits = 2)%>% mutate(Date = as.Date(paste0("2018-", 06, "-01"), "%Y-%m-%d"))
  
  BiomeT_June2019 <- BC_June2019 %>% filter(BIOME == 'T')%>% group_by(TYPE_E)%>% summarise(area_des_ha = as.numeric(sum(O_AREA)) * 1e-4) %>%
    mutate(percent_des = (area_des_ha * 1e4) / as.numeric(sum(BC_Dec2019$O_AREA)) * 100) %>% mutate_if(is.numeric, round, digits = 2)%>%
     mutate(Date = as.Date(paste0("2019-", 06, "-01"), "%Y-%m-%d"))
  
  BiomeT_Dec2019 <- BC_Dec2019 %>% filter(BIOME == 'T')%>% group_by(TYPE_E)%>% summarise(area_des_ha = as.numeric(sum(O_AREA)) * 1e-4) %>%
    mutate(percent_des = (area_des_ha * 1e4) / as.numeric(sum(BC_Dec2019$O_AREA)) * 100) %>% mutate_if(is.numeric, round, digits = 2)%>% 
    mutate(Date = as.Date(paste0("2019-", 12, "-01"), "%Y-%m-%d"))
  
#  Transform each spatial object to B.C projection crs
  
  BiomeT_June2018 <- transform_bc_albers(BiomeT_June2018)
  BiomeT_June2019 <- transform_bc_albers(BiomeT_June2019)
  BiomeT_Dec2019 <- transform_bc_albers(BiomeT_Dec2019)
  
# combine spatial objects for ploting
  BiomeT_combined <- rbind(BiomeT_June2018, BiomeT_June2019, BiomeT_Dec2019)
  
  # plot spatial objects
  
  tm_shape(BiomeT_combined) +
    tm_polygons()+
    tm_symbols(col = "black", border.col = "white", size = "area_des_ha") +
    tm_facets(by = "Date", nrow = 2, free.coords = FALSE)
  

```



# The map above can be veiwing our map interactively using mapview and leaflet from below

```{r}

 map_BC <- tm_shape(BiomeT_combined) +
    tm_polygons()+
    tm_symbols(col = "black", border.col = "white", size = "area_des_ha") +
    tm_facets(by = "Date", nrow = 2, free.coords = FALSE)

tmap_mode("view")

map_BC

```
```{r}
BiomeT_combined %>%
   filter(TYPE_E == "Protected Area") %>% st_collection_extract("POLYGON") %>% 
  mapview(color = "red", lwd = 3, layer.name = "TYPE_E")
  
```



```{r}
pal = colorNumeric("RdYlBu", domain = BiomeT_combined$percent_des)

leaflet(data = BiomeT_combined) %>% 
  addPolygons(data = BiomeT_combined, fill = TRUE) %>%
  addLegend(pal = pal, values = ~percent_des) %>%
  setView(lng = -0.1, 51.5, zoom = 12) %>% 
  addMiniMap()
  
```

# A useful shortcut to Mapping Applications with Shiny
```{r}
library(shiny)    # for shiny apps
library(leaflet)  # renderLeaflet function
library(bcmaps)

ui = fluidPage(
  sliderInput(inputId = "area_des_ha", "Area designated", 0, 1045.21, value = 80),
      leafletOutput(outputId = "map")
  )
server = function(input, output) {
  output$map = renderLeaflet({
       BiomeT_combined %>% 
      tm_shape() +
    tm_polygons()+
    tm_symbols(col = "black", border.col = "white", size = input$area_des_ha) +
    tm_facets(by = "Date", nrow = 2, free.coords = FALSE) })
}
shinyApp(ui, server)
```

